%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Abbishek}{P.M.}{ \urlstyle{same}\href{https://www.abbishek.in}{abbishek.in} \\
\href{mailto:abbishekpm@gmail.com}{abbishekpm@gmail.com} | +91 9611631086
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Vellore Institute of Technology}
\descript{Master of Computer Application}
\location{Dec 2025 | Chennai, India}
\sectionsep

\subsection{Global Institute of Management Sciences College}
\descript{Bachelor of Computer Applications}
\location{Mar 2022 | Bangalore, India}
CGPA: 6.65 / 10.0}
\sectionsep

\subsection{Baldwin Co-Education PU College}
\location{PUC. May 2018|  Bangalore, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://www.facebook.com/abbishekpm}{\bf abbishekpm} \\
Github:// \href{https://www.github.com/abbishekprabhu}{\bf abbishekprabhu} \\
LinkedIn://  \href{https://www.linkedin.com/in/abbishekprabhu}{\bf abbishekprabhu} \\
Twitter://  \href{https://www.x.com/abbishekoffl}{\bf @abbishekoffl} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\textbullet{} HTML \textbullet{} CSS \textbullet{} Python \textbullet{} Javascript 
\textbullet{}jQuery \textbullet{} Figma \textbullet{} Oracle SQL \textbullet{} React.js\ 
Next.js \textbullet{} Gatsby.js \textbullet{} Tailwind CSS \textbullet{} Netlify  \textbullet{} Vercel 
\textbullet{}API \textbullet{} Axios \\\textbullet{} Product Management \\ \textbullet{} Project Management \textbullet{} Communication \\ \textbullet{} Agile
\sectionsep
\section{Languages} 
\textbullet{} English \textbullet{} Tamil \textbullet{} Kannada \textbullet{} Telugu

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Alpha and Omega}
\descript{| UI / UX Developer }
\location{Aug 2023 - Present | Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed and developed a cutting-edge website for them and managing it.
\item Managed social media by posting videos and photos. 
\end{tightemize}
\sectionsep

\runsubsection{Pepul}
\descript{| Software Engineer - Frontend }
\location{Aug 2022 – Aug 2023 | Chennai, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Crafted a website showcasing an innovative AI app, starting from ground zero.
\item Developed an animated landing page that elevates Pepul Creators’ online presence.
\item Pioneered a cutting-edge EV campaign page.
\item Developed a page called Co-Creation.
\item Developed Co-creation's first project- Adityaram.
\item Coded a cutting-edge Shops Near Me landing page.
\item Developed a HRM Dashboard for Pepul.
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certificate}
\runsubsection{Pyspiders}
\descript{| Python Fullstack development course}
\location{Jan 2022 – Aug 2022 | Bangalore, India}
 \textbullet{} HTML \textbullet{} CSS \textbullet{} JavaScript \textbullet{} Bootstrap \textbullet{} Python \textbullet{} Oracle SQL \textbullet{} Django
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Volunteering} 
\runsubsection{CISO Platform}
\descript{| Student Volunteer }
\location{Feb 2020 – Feb 2020 | Bangalore, India}
\begin{tightemize}
\item I was volunteering for a meeting from this company and got to see many great people!
\end{tightemize}

\section{Projects} 
\runsubsection{Techfolio}
\descript{| My Own Portfolio }
{The Techfolio is a meticulously researched, thoughtfully designed, and developer-friendly portfolio. It is reusable and tailored for developers proficient in Figma. The portfolio can be accessed on GitHub.}
 \\\location{Skills - HTML, CSS, JavaScript, Git, GitHub, GitHub Pages.}
 \vspace{\topsep}
 \runsubsection{SV Events}
\descript{| A Gatsby Project }
{I developed a captivating event website using Gatsby JS for an event company, delivering a seamless user experience and showcasing their services in an engaging manner.}
 \\\location{Skills - Gatsby.js, CSS, Git, GitHub, Netlify.}
  \vspace{\topsep}
 \runsubsection{Squareball - the fitness arena}
\descript{| A Creative Design and Development project }
{I designed and developed a captivating static website using FIGMA, HTML, CSS, JS for a GYM, delivering a seamless user experience and showcasing their services in an engaging manner.}
 \\\location{Skills - HTML, CSS, JS, jQuery, Figma, GIT, Github, Netlify}
\end{minipage} 
\end{document}  \documentclass[]{article}
